Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
conclusion

We have presented a QBF-based method that reduces the number of
acceptance marks in transition-based Emerson-Lei automata. The method
has ben implemented and our experimental results show that

chceme sem napsat, ze QBF-based reduction se da pouzit napr. k
nalezeni akceptacni formule s $c$ klauzulemi a $m$ znackami v CNF,
pripadne k nalezeni ekvivalentniho paritniho automat s danou maximalni
paritou $p$ a stejnou strukturou. Nebo zkusit nalezt $\Fin$-less
acceptance formuli.

Redukce netrva vecne, da se prakicky pouzit a zkracenim timeoutu na
QBF-solver se da zrychlit (tradeoff s ucinnosti). Prinejmensim u
Rabinizeru 4 je velmi dobra sance, ze se to vyplati. Pridat do
experimentu nejaky graf, ktery ukaze, jak rychle se nektere automaty
redukovaly na minimum?

>>>>

We have presented a QBF-based method that reduces the number of
acceptance marks in transition-based Emerson-Lei automata. The method
has been implemented and our experimental results show that it is possible
to use the QBF solvers to find equivalent acceptance conditions of TELA
without changes to their structure.
The reduction of acceptance marks is not the only purpose of the approach,
one could possibly look for e.g. equivalent parity automata or automata without
$\Fin$-marks, depending on the subsequent use of the automata.
Even though the QBF queries can be time-consuming, in practice it can be well
used and one can find a good trade-off between speed and efficiency by setting
a reasonable timeout.

In the future work, it could be examined how the reductions of the acceptance
condition can contribute to further reduction of the state space by enabling
various optimizations, e.g. simulations.
